Implications of afforestation policies for global markets

### 2024-02-26 paper.Rmd
Update paper.Rmd

When we examine how this impacts exports of agricultural goods, we find that Japan and the United States appear to be the biggest beneficiaries of this policy with their exports increasing 13.5 percent and 5.0 percent, respectively (table 3). The regions where agricultural exports drop most significantly are South Asia, Southeast Asia, and Central America who see decreases of 11.0 percent, 7.3 percent, and 6.9 percent, respectively.

Table 3 qxw-Ag
				∆ (%)
				Agriculture
East Asia			-5.1
Southeast Asia			-2.0
Central America			-2.0
South Asia			-1.1
North Africa & the Middle East	-0.9
Sub-Saharan Africa		-0.3
China				-0.1
Russia				0.1
Brazil				0.2
Rest of South America		-1.2
West & Central Europe 		0.4
United States			0.6
Oceania				0.7
Canada				1.3
Japan				1.4

@@

Table 4 EV
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
EUII				-588,500,000
Brazil				-735,125,000
United States			-1,085,000,000
Russia				-1,152,375,000
Rest of South America		-3,848,625,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
European Union			-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any positive price impacts resulting from this policy, with the price of agricultural goods decreasing 0.2 percent (table 5). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.1 and 2.8 percent.

Table 5 pm
									∆ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania					0.6	0.3	0.3	0.3	0.3
China					0.7	0.3	0.2	0.2	0.3
Japan					-0.2	0.2	0.2	0.2	0.2
East Asia				2.8	0.2	0.2	0.2	0.2
Southeast Asia				1.5	0.2	0.2	0.2	0.2
South Asia				1.6	0.2	0.2	0.1	0.2
Canada					0.4	0.3	0.3	0.3	0.4
United States				0.4	0.3	0.3	0.3	0.3
Central America				1.3	0.2	0.2	0.2	0.2
Brazil					0.7	0.3	0.3	0.3	0.3
Rest of South America			1.1	0.2	0.2	0.2	0.2
European Union				0.5	0.2	0.2	0.2	0.2
EUII					0.6	0.3	0.2	0.2	0.2
Russia					0.6	0.2	0.2	0.2	0.2
Sub-Saharan Africa			0.9	0.3	0.2	0.2	0.3
North Africa & the Middle East		1.1	0.2	0.2	0.2	0.2

>>>>

When we examine how this impacts exports of agricultural goods, we find that Japan and the United States appear to be the biggest beneficiaries of this policy with their exports increasing 8.8 percent and 3.5 percent, respectively (table 3). The regions where agricultural exports drop most significantly are East Asia, South Asia, Southeast Asia, and Central America who see decreases of 14.5 percent, 5.9 percent, 5.1 percent,and 5.0 percent, respectively.

Table 3 qxw-Ag
				∆ (%)
				Agriculture
Japan				8.78
United States			3.49
Canada				3.13
China				1.96
Oceania				1.67
Russia				1.52
West & Central Europe 		1.16
Brazil				1.03
Rest of South America		-2.67
Sub-Saharan Africa		0.02
North Africa & the Middle East	-1.52
Central America		-5.02
Southeast Asia		-5.14
South Asia		-5.94
East Asia		-14.45

@@

Table 4 EV
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
EUII				-588,500,000
Brazil				-735,125,000
United States			-1,085,000,000
Russia				-1,152,375,000
Rest of South America		-3,848,625,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
West & Central Europe		-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any positive price impacts resulting from this policy, with the price of agricultural goods decreasing 0.3 percent (table 5). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.3 and 5.1 percent.

Table 5 pm
									∆ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania						1.2	0.4	0.5	0.5	0.5
China						1.1	0.4	0.4	0.4	0.4
Japan						-0.3	0.4	0.4	0.4	0.4
East Asia					5.1	0.3	0.3	0.3	0.4
Southeast Asia					2.8	0.3	0.3	0.4	0.3
South Asia					3.1	0.3	0.3	0.3	0.3
Canada						0.7	0.5	0.5	0.5	0.5
United States					0.7	0.5	0.5	0.5	0.5
Central America					2.5	0.3	0.3	0.4	0.3
Brazil						1.2	0.5	0.5	0.5	0.5
Rest of South America				2.1	0.3	0.3	0.3	0.3
West & Central Europe 				0.9	0.4	0.4	0.4	0.4
Russia						1.1	0.4	0.4	0.4	0.4
Sub-Saharan Africa				1.5	0.4	0.4	0.4	0.4
North Africa & the Middle East			2.0	0.4	0.4	0.4	0.4
